PANNEURO_analysis

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
probable_covid_all

# Demographics
## Ethnicity_collapsed
### Pie charts
**NEED TO CREATE ETHNICITY_collapsed variable**
```{r Ethnicity_collapsed prop per total summary}
Ethnicity_collapsed_prop_Covid <- dat.raw %>%
  count(Ethnicity_collapsed, covid_probable_case_incl_screening) %>%
  drop_na() %>%
  mutate(freq = round(n/sum(n), 2))

# total responders
ethN <- sum(Ethnicity_collapsed_prop_Covid$n)

kable(Ethnicity_collapsed_prop_Covid)
Ethnicity_collapsed_prop_Covid
```

pie chart with only European label

```{r ethnicity pie chart biggest group label}
eth_pie_alllabel <- 
  Ethnicity_collapsed_prop_Sample %>%
   mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%

  ggplot(aes(x="", y=freq, fill=Ethnicity_collapsed)) +
  geom_bar(width = 1, stat = "identity") +
  scale_fill_manual(values =  COPINGpalette6) +
  scale_color_manual(values =  COPINGpalette6) +
  coord_polar("y",start=0) +
  theme_void() +
   labs(title = paste("RAMP/COPING sample self reported ethnicity",
                      sep=" "),
        subtitle = paste("n =", sum(Ethnicity_collapsed_prop_Sample$n),
                         sep = " "),
        fill = "Self reported ethnicity")  +
    geom_text(aes(y = c(0.5),
                  label= c(paste0(round((freq[1]*100),0),"%"))), #Frequency of European only
             size=5,
             face="bold"
             )

eth_pie_alllabel
```

Pie chart - no labels

```{r ethnicity pie chart no label}
eth_pie_nolabel <- 
  Ethnicity_collapsed_prop_Sample %>%
   mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%

  ggplot(aes(x="", y=freq, fill=Ethnicity_collapsed)) +
  geom_bar(width = 1, stat = "identity") +
  scale_fill_manual(values =  COPINGpalette6) +
  scale_color_manual(values =  COPINGpalette6) +
  coord_polar("y",start=0) +
  theme_void() +
   labs(title = paste("RAMP/COPING sample self reported ethnicity",
                      sep=" "),
        subtitle = paste("n =", sum(Ethnicity_collapsed_prop_Sample$n),
                         sep = " "),
        fill = "Self reported ethnicity")

eth_pie_nolabel
```

@@

```{r neurological frequencies nmss}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  group_by(covid_test_positive) %>%
  select(
    starts_with("nmss"),
    -ends_with("numeric")
  ) %>% 
  colnames()
```

```{r neurological frequencies nmss.ability_taste_food_smell}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(nmss.ability_taste_food_smell)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, nmss.ability_taste_food_smell) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies nmss.severe_taste_smell_loss}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(nmss.severe_taste_smell_loss)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, nmss.severe_taste_smell_loss) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies nmsw}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  group_by(covid_test_positive) %>%
  select(
    starts_with("nmsw"),
    -ends_with("numeric")
  ) %>% 
  colnames()
```

```{r neurological frequencies nmsw.drink_problems_choking_difficulty}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(nmsw.drink_problems_choking_difficulty)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, nmsw.drink_problems_choking_difficulty) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies nmsw.regularly_night_pass_urine}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(nmsw.regularly_night_pass_urine)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, nmsw.regularly_night_pass_urine) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies nmsw.sex_difficult_finding}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(nmsw.sex_difficult_finding)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, nmsw.sex_difficult_finding) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies nmsw.weak_standing_feeling_light}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(nmsw.weak_standing_feeling_light)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, nmsw.weak_standing_feeling_light) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies nmsw.acting_moving_sleep_talking}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(nmsw.acting_moving_sleep_talking)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, nmsw.acting_moving_sleep_talking) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies nmsw.double_vision}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(nmsw.double_vision)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, nmsw.double_vision) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies tinnitus}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  group_by(covid_test_positive) %>%
  select(
    starts_with("tinnitus"),
    -ends_with("numeric")
  ) %>% 
  colnames()
```

```{r neurological frequencies tinnitus.ears_noises_minutes_head}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(tinnitus.ears_noises_minutes_head)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, tinnitus.ears_noises_minutes_head) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies tinnitus.ears_noises_minutes_head_frequency}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(tinnitus.ears_noises_minutes_head_frequency)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, tinnitus.ears_noises_minutes_head_frequency) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies tinnitus.noises_worry_worst_upset}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(tinnitus.noises_worry_worst_upset)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, tinnitus.noises_worry_worst_upset) %>%
  mutate(Prop = round(n/sum(n), 2))
```

**ADD SCORING FOR NEURO MEASURES**
# ALSfrs
```{ALSfrs col names r}
als.col.names <- dat.raw %>%
  select(
    starts_with("alsfrs") & ends_with("numeric")
  ) %>%
  colnames()

@@

```{r nmsw col names}
nmsw.col.names <- dat.raw %>%
  select(
    starts_with("nmsw") & ends_with("numeric")
  ) %>% 
  colnames()
nmsw.col.names

```{r scoring NMSW}
dat.raw <- dat.raw %>% 
  mutate(nmsw.sum_score = 
           rowSums(select(.,nmsw.col.names), na.rm = FALSE)
           )

>>>>

@@

```{r neurological frequencies nmss}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  select(
    starts_with("nmss"),
    -ends_with("numeric")
  ) %>% 
  colnames()
```

```{r neurological frequencies nmss.ability_taste_food_smell}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(nmss.ability_taste_food_smell)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, nmss.ability_taste_food_smell) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies nmss.severe_taste_smell_loss}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(nmss.severe_taste_smell_loss)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, nmss.severe_taste_smell_loss) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies nmsw}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  select(
    starts_with("nmsw"),
    -ends_with("numeric")
  ) %>% 
  colnames()
```

```{r neurological frequencies nmsw.drink_problems_choking_difficulty}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(nmsw.drink_problems_choking_difficulty)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, nmsw.drink_problems_choking_difficulty) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies nmsw.regularly_night_pass_urine}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(nmsw.regularly_night_pass_urine)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, nmsw.regularly_night_pass_urine) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies nmsw.sex_difficult_finding}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(nmsw.sex_difficult_finding)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, nmsw.sex_difficult_finding) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies nmsw.weak_standing_feeling_light}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(nmsw.weak_standing_feeling_light)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, nmsw.weak_standing_feeling_light) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies nmsw.acting_moving_sleep_talking}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(nmsw.acting_moving_sleep_talking)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, nmsw.acting_moving_sleep_talking) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies nmsw.double_vision}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(nmsw.double_vision)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, nmsw.double_vision) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies tinnitus}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  select(
    starts_with("tinnitus"),
    -ends_with("numeric")
  ) %>% 
  colnames()
```

```{r neurological frequencies tinnitus.ears_noises_minutes_head}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(tinnitus.ears_noises_minutes_head)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, tinnitus.ears_noises_minutes_head) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies tinnitus.ears_noises_minutes_head_frequency}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(tinnitus.ears_noises_minutes_head_frequency)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, tinnitus.ears_noises_minutes_head_frequency) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies tinnitus.noises_worry_worst_upset}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(tinnitus.noises_worry_worst_upset)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, tinnitus.noises_worry_worst_upset) %>%
  mutate(Prop = round(n/sum(n), 2))
```

**ADD SCORING FOR NEURO MEASURES**

# ALSfrs
```{ALSfrs col names r}
als.col.names <- dat.raw %>%
  select(
    starts_with("alsfrs") & ends_with("numeric")
  ) %>%
  colnames()

@@
